### 2018-02-05 thesis/contents/tn_sagit.tex
Updates from ShareLaTeX

\textbf{Results:} Both affected and unaffected trigeminal nerves in TN patients can be differentiated with 80\% accuracy from controls. Affected CN V FA segments that are differentiated from trons have more overlap towards the distal segments in the cistern and gangion, whereas unaffected CN V segment overlaps extend more towards the brainstem. The bilateral middle segment of S1 can be differentiated from controls. Where the affected S1 RD classifier achieved higher accuracy of 87\%.

>>>>

\textbf{Results:} Both affected and unaffected trigeminal nerves in TN patients can be differentiated with 80\% accuracy from controls. Affected CN V FA segments that are differentiated from controls have more overlap towards the distal segments in the cistern and gangion, whereas unaffected CN V segment overlaps extend more towards the brainstem. Bilateral TPT differ from controls with at least 85\%. TPT left-right classification achieved 98\%. The bilateral middle segment of S1 can be differentiated from controls. Where the affected S1 RD classifier achieved higher accuracy of 87\%.
